Efficient evaluation of threshold queries of derived fields in a numerical simulation database

### 2014-08-14 paper.tex
Work on experiments section.

\section{Scientific Use Cases}
Max vorticity clustering.

@@

-- measure the overhead of querying the cache first

>>>>

\section{Scientific Use Cases}\label{science_use_cases}
Max vorticity clustering.

@@

For this evaluation we looked at the performance of threshold queries to the vorticity field. The vorticity field is representative of derived fields, which
have to be computed from the stored data. The vorticity is computed from the velocity field by taking its curl. As described in section \ref{science_use_cases}
thresholding the vorticity field is important in the study of fluid dynamics and clustering the locations of maximum vorticity can lead to new insights into
the development of the most intense vortices that are observed. [TODO: Consider showing other fields as well; possibly thresholding the velocity by itself]

-- measure the overhead of querying the cache first:
Figure showing avg. execution times of queries for vorticity with a high threshold, medium threshold and low threshold. For each threshold value
plot the time to simply do the I/O, the time the query takes without the presence of a cache (the difference is essentially the time taken to compute
the vorticity field at each location on the grid) and the time the query takes with the inclusion of a cache. This shows that the overhead associated
with querying and updating the cache is not significant. Consider including a figure for a representative time-step showing the PDF of the vorticity field
to show how the vorticity values are distributed and to get an understanding for the different threshold levels.
